---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(MASS)
library(ggplot2)
library(vtable)
library(stargazer)
library(estimatr)
library(dplyr)
library(tidyr)
library(here)

### Directory
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) #Set's directory where script is located
getwd()

# IMPORT CSV DATA
CGL <- read.csv(here("data", "cgl_collapse_data_extract.csv"))

# SUMMARY STATISTICS
stargazer(CGL, type="text", digits=2)

```

```{r}
# EXAMINE BALANCE IN COVARIATES
# COVARIATE MEAN DIFFERENCES by DAPever
m1 <- lm(formula = LME ~ DAPever, data=CGL)
m2 <- lm(formula = genus ~ DAPever, data=CGL)
m3 <- lm(formula = species ~ DAPever, data=CGL)
se_models = starprep(m1, m2, m3, stat = c("std.error"), se_type = "HC2", alpha = 0.05)
stargazer(m1, m2, m3, se = se_models, type="text")
```

```{r}
# BOXPLOTS TO EXAMINE BALANCE IN COVARIATES
ggplot(CGL, aes(x=as.factor(DAPever), y=LME)) + 
  geom_boxplot(fill="cyan") + xlab("Ever Collapsed")

ggplot(CGL, aes(x=as.factor(DAPever), y=genus)) + 
  geom_boxplot(fill="cyan") + xlab("Ever Collapsed")

ggplot(CGL, aes(x=as.factor(DAPever), y=species)) + 
  geom_boxplot(fill="cyan") + xlab("Ever Collapsed")
```

0 means no ITQ, 1 means yes ITQ. For LME, The median value is around 35 for untreated ITQs; it is similar in ITQs for treated, but there is not as much mass around the median, which is problematic for comparing the 2. 

Similar distributions for genus in treated and untreated fisheries, and same for species. 


Below, we are applying ignorabilty, like applying the regression with the 12,000 veteran variables... but we are not interacting the variables here. 
```{r}
# BASIC OLS by DAPever -- THEN ADD INDICATORS FOR OTHER COVARIATES 
# NOTE DO NOT INCLUDE SPECIES IN MODELS TO KEEP RUNNING TIME FAST
mA <- lm(formula = collapse ~ DAPever, data=CGL)
mB <- lm(formula = collapse ~ DAPever + as.factor(LME), data=CGL)
mC <- lm(formula = collapse ~ DAPever + as.factor(LME) + as.factor(genus), data=CGL)
se_models = starprep(mA, mB, mC, stat = c("std.error"), se_type = "HC2", alpha = 0.05)
stargazer(mA, mB, mC, se = se_models, type="text", omit = "(LME)|(genus)|(species)")
```
DAPever in the output above represents the difference between mean of Y when D = 1 and mean of Y when D = 0. 


```{r}
# BASIC PROPENSITY SCORE --- THIS IS A TOY MODEL
# ESTIMATE PROPENSITY SCORE MODEL AND PREDICT (EPS)
ps_model <- glm(DAPever ~ LME + genus, family = binomial(), data = CGL)
summary(ps_model)
EPS <- predict(ps_model, type = "response") #here we are using the estimated 
PS_WGT <- (CGL$DAPever/EPS) + ((1-CGL$DAPever)/(1-EPS)) #defining the weight for the regression analysis 


# COLLECT ALL RELEVANT VARIABLES IN DATAFRAME
DF <- data.frame(years = CGL$years, collapse = CGL$collapse, DAPever = CGL$DAPever, 
                 LME = CGL$LME, genus = CGL$genus, species = CGL$species, EPS, PS_WGT)
```

```{r}
# BOXPLOTS TO EXAMINE OVERLAP IN P-SCORE DISTRIBUTIONS
ggplot(DF, aes(x=as.factor(DAPever), y=EPS)) + 
  geom_boxplot(fill="cyan") + xlab("Ever Collapsed")
```

```{r}
# WLS USING EPS WEIGHTS
wls1 <- lm(formula = collapse ~ DAPever, data=DF, weights=PS_WGT) 
wls2 <- lm(formula = collapse ~ DAPever + LME + genus, data=DF, weights=PS_WGT) #add linear controls for the characteristics 
se_models = starprep(wls1, wls2, stat = c("std.error"), se_type = "HC2", alpha = 0.05)
stargazer(wls1, wls2, se = se_models, type="text", omit = "(LME)|(genus)|(species)")
```
The adjustment almost doesn't change the output: tells us there is either no bias or the weights did not do much to control for bias. 